Bare minimum: order theory

### 2025-09-21 BareMinima/OrderTheory/BareMinimumOrderTheory.tex
OrderTheory: fixed left margin notes

\begin{defn}[Lattice - order theoretic]
	A \textbf{lattice} \marginleft{Lattice} is a partially ordered set in which every pair of elements has both a supremum/join and an infimum/meet. A \textbf{sublattice} is a subposet of a lattice.
\end{defn}

@@

\begin{defn}[Lattice - algebraic]
	An algebraic \marginleft{Lattice (algebraic)} structure $(X, \vee, \wedge)$ consisting of a set $X$ and two binary operations $\vee$ and $\wedge$ is an \textbf{(algebraic) lattice} if it satisfies the following properties:
	\begin{description}
		\item[Associativity] $(a \vee b) \vee c = a \vee (b \vee c)$
		and $(a \wedge b) \wedge c = a \wedge (b \wedge c)$
		\item[Commutativity] $a \vee b = b \vee a$
		and $a \wedge b = b \wedge a$
		\item[Idempotency] $a \vee a = a$
		and $a \wedge a = a$
		\item[Absorption] $a \vee (a \wedge b) = a$
		and $a \wedge (a \vee b) = a$
	\end{description}
\end{defn}

@@

\begin{defn}[Boolean algebra]
	An algebraic \marginleft{Boolean algebra} structure $(X, \vee, \wedge, \neg, \bot, \top)$ is a \textbf{Boolean algebra} if it satisfies the following properties:
	\begin{description}
		\item[Lattice] $(X, \vee, \wedge)$ is a lattice
		\item[Distributivity] $a \vee (b \wedge c) = (a \vee b) \wedge (a \vee b)$
and $a \wedge (b \vee c) = (a \wedge b) \vee (a \wedge b)$
		\item[Identity] $a \vee \bot = a$
		and $a \wedge \top = a$
		\item[Complementation] $a \vee \neg a = \top$
		and $a \wedge \neg a = \bot$
	\end{description}
\end{defn}

@@

\begin{defn}
	A \textbf{Heyting algebra} \marginleft{Heyting algebra} is a bounded lattice for which the relative pseudo-complement always exists.
\end{defn}

@@

\begin{defn}
	Given a poset $(X, \leq)$ a \textbf{closure operator} is a map $cl : X \to X$ that satisfies the following for all $a,b \in X$:
	\begin{enumerate}
		\item \textbf{extensive}: $a \leq cl(a)$
		\item \textbf{increasing}: $a \leq b \implies cl(a) \leq cl(b)$
		\item \textbf{idempotent}: $cl(cl(a)) = cl(a)$.
	\end{enumerate}
\end{defn}

@@

\begin{defn}
	Given a set $S$, an \textbf{intersection structure}, or $\bigcap$-structure, on $S$ is a family $X \subseteq 2^{S}$ of subsets of $S$ that is closed under arbitrary intersection. That is, $\bigcap A_i \in X$ for every non-empty family $A_i \in X$. A topped intersection structure on $S$ is an intersection structure such that $S \in X$.
\end{defn}

>>>>

\begin{defn}[Lattice - order theoretic]
	A \textbf{lattice} \marginleft{Lattice \\ (order)} is a partially ordered set in which every pair of elements has both a supremum/join and an infimum/meet. A \textbf{sublattice} is a subposet of a lattice.
\end{defn}

@@

\begin{defn}[Lattice - algebraic]
	An algebraic \marginleft{Lattice \\(algebra)} structure $(X, \vee, \wedge)$ consisting of a set $X$ and two binary operations $\vee$ and $\wedge$ is an \textbf{(algebraic) lattice} if it satisfies the following properties:
	\begin{description}
		\item[Associativity] $(a \vee b) \vee c = a \vee (b \vee c)$
		and $(a \wedge b) \wedge c = a \wedge (b \wedge c)$
		\item[Commutativity] $a \vee b = b \vee a$
		and $a \wedge b = b \wedge a$
		\item[Idempotency] $a \vee a = a$
		and $a \wedge a = a$
		\item[Absorption] $a \vee (a \wedge b) = a$
		and $a \wedge (a \vee b) = a$
	\end{description}
\end{defn}

@@

\begin{defn}[Boolean algebra]
	An algebraic \marginleft{Boolean \\ algebra} structure $(X, \vee, \wedge, \neg, \bot, \top)$ is a \textbf{Boolean algebra} if it satisfies the following properties:
	\begin{description}
		\item[Lattice] $(X, \vee, \wedge)$ is a lattice
		\item[Distributivity] $a \vee (b \wedge c) = (a \vee b) \wedge (a \vee b)$
and $a \wedge (b \vee c) = (a \wedge b) \vee (a \wedge b)$
		\item[Identity] $a \vee \bot = a$
		and $a \wedge \top = a$
		\item[Complementation] $a \vee \neg a = \top$
		and $a \wedge \neg a = \bot$
	\end{description}
\end{defn}

@@

\begin{defn}
	A \textbf{Heyting algebra} \marginleft{Heyting \\ algebra} is a bounded lattice for which the relative pseudo-complement always exists.
\end{defn}

@@

\begin{defn}
	Given a poset $(X, \leq)$ \marginleft{Closure} a \textbf{closure operator} is a map $cl : X \to X$ that satisfies the following for all $a,b \in X$:
	\begin{enumerate}
		\item \textbf{extensive}: $a \leq cl(a)$
		\item \textbf{increasing}: $a \leq b \implies cl(a) \leq cl(b)$
		\item \textbf{idempotent}: $cl(cl(a)) = cl(a)$.
	\end{enumerate}
\end{defn}

@@

\begin{defn}
	Given a set $S$, \marginleft{Intersection \\structure} an \textbf{intersection structure}, or $\bigcap$-structure, on $S$ is a family $X \subseteq 2^{S}$ of subsets of $S$ that is closed under arbitrary intersection. That is, $\bigcap A_i \in X$ for every non-empty family $A_i \in X$. A topped intersection structure on $S$ is an intersection structure such that $S \in X$.
\end{defn}
